### 2019-07-08 README.rmd
updates and renders README

<!-- Code status -->
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=dev)](https://travis-ci.org/ProvTools/Rclean)

>>>>

<!-- Code status -->
[![Dev: Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=tests)](https://travis-ci.org/ProvTools/Rclean) 
[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/tests/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=tests)
